Secure Composition of Robust and Optimising Compilers

### 2023-07-08 popl/main.tex
Draft: Abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  \hltt{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}

  Secure compilers emit code that is hardened against adversarial target--level attacks, such as memory corruption or alteration of control--flow.
  It is an open question wether secure compilers compose in a well--behaved manner.
  This paper answers this question positively: The composition of compilers that are secure with respect to some security--properties yields the intersection of these properties.
  This article discusses different variants of compositions of secure compilers in a formal manner and instantiates parts of these results in a case--study.
  To this end, an optimizing, secure compilation chain that preserves both memory safety and cryptographic constant time is presented.
  Memory safety is achieved by composing secure compilers for both temporal and spatial memory safety, where the compiler for spatial memory safety is an instrumentation that inserts bounds--checks in front of pointer dereferences.
  The compiler for cryptographic constant time exploits the use of a data (operand) timing independent mode and the employed optimisations of the compilation chain are constant folding and dead code elimination.
  The compositionality results enable modular proofs for the whole compilation chain that is secure with respect to both memory safety and cryptographic constant time.
